EpisoPass: Password Management based on Episodic Memories

### 2016-12-11 paper/Password2016/cameraready.tex
...

\usepackage{url}
% \urldef{\mailsa}\path|masui@pitecan.com|
\urldef{\mailsa}\path|***@***.***.***|
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

@@

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
% \author{Toshiyuki Masui%
\author{***** ****
% \thanks{Thanks...}%
}
%
\authorrunning{Lecture Notes in Computer Science: Authors' Instructions}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
%\institute{Faculty of Environment and Information Studies, Keio University\\
%5322 Endo, Fujisawa, Kanagawa 252-8520, Japan\\
%\mailsa\\
%\url{http://pitecan.com/}}
\institute{******* ******* ******* *******\\
******, ****** *******, *******\\
\mailsa\\
% \url{http://pitecan.com/}}
\url{http://*****.***.***/}}

@@

When the user clicks on different candidate answers 
the seed string is converted to a completely different strings, such as
``\textsf{Xvdkzb940345}'', as shown in Figure \ref{web11}.

@@

@@

When the secret string is changed to ``\textsf{Facebook123456}'',
the generated password changes to ``\textsf{Onjbrppy030937}'',
as shown in Figure \ref{web2}.
In this way, the user can generate different passwords for
different services just by changing the seed string.

@@

% \marginnote{The fact that an `old' memory is unlikely to be forgotten
%   is perhaps obvious, but this could be a good place to cite a paper
%   on memory/psychology about this if you're aware of any?}

@@

It can be difficult to provide a large number of false answers to a question like
``what is your favorite sport?''
because the number of possible answers is limited.
%
On the other hand, if the right answer to the question is a name of a place or a person,
generating similar answers is straightforward.
For example, if the answer to the question is ``Colorado'',
we can easily provide fake answers like ``California'', ``Utah'', etc.
because we can use the list of states in the U.S. as possible answers.

@@

% \marginnote{It may be helpful to give an indication of how many Q-A sets you think
% would be considered `sufficient' here.}
%
To prevent this, it is safer to keep all of the questions and answers
in a secret place or
use sufficient questions to prevent such a brute-force attack from being viable.

@@

Answering to many questions takes much longer time than typing a
remembered password, so most people may prefer typing password
rather than using EpisoPass if they have to log in to a service frequently.
The tradeoff betwee security and usability has long been a big issue
of authentication systems \cite{Braz:2007:DTU:1778331.1778344},
but we believe we can approach the best solution by
improving the user interface of answering questions.

@@

The EpisoPass service is available via the Website and the source code is
available on GitHub\footnote{
  (url removed for double-blind review)
  % \url{https://EpisoPass.com/},
  % \url{https://github.com/masui/EpisoPass}
}. EpisoPass currently has only a small user-base, one major
reason being that most people cannot fully understand the
idea behind EpisoPass, and may not trust it without the 
support of a well-known IT company.
% nor supported by famous computer users.
Another reason is that it's difficult for users to
assess the security of EpisoPass.
Since the intention is for the questions and answers to be obvious
to those that know them (but not to others), users may lack
confidence in their answers being unknown to others.
Any authentication system expecting widespread use must take
such psychological issues seriously, and we hope to address 
such issues in future work.

@@

\subsection*{Note.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \subsection{Citations}

% \marginnote{I've added some text in about the grant. Please change it
%   as you see fit of course. I'm afraid I don't know the grant number
%   so have left a gap; ideally this should be added in too.}

% \subsubsection*{Acknowledgments.}
% This paper was written while on
% sabbatical at the University of Cambridge, hosted by Frank Stajano and
% the Pico group, and supported by EPSRC grant number
% EPSRC IRIS grant EP/M019055/1 on  ``Future Authentication Systems''.

\bibliographystyle{splncs03}
\bibliography{paper}

>>>>

\usepackage{url}
\urldef{\mailsa}\path|masui@sfc.keio.ac.jp|
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

@@

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Toshiyuki Masui%
% \thanks{Thanks...}%
}
%
\authorrunning{Lecture Notes in Computer Science: Authors' Instructions}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{Faculty of Environment and Information Studies, Keio University\\
5322 Endo, Fujisawa, Kanagawa 252-8520, Japan\\
\mailsa\\
\url{http://pitecan.com/}}

@@

When the user clicks on different candidate answers 
the seed string is converted to a completely different string, such as
``\textsf{Xvdkzb940345}'', as shown in Figure \ref{web11}.

@@

% Frank:
% This is a very overconstraining way of saying ``upper, lower and
% digits''. First, it says ``one upper, five lower, six
% digits''. Second, it puts them in specific places. Aren't you being a
% lot more prescriptive than the site's own policy? This reduces the
% space of passwords that can be generated, for very little benefit.
%
% そうかな? まぁ言いたいことはわかるけど

@@

When the secret string is changed to ``\textsf{Facebook123456}'',
the generated password changes to ``\textsf{Onjbrppy030937}'',
as shown in Figure \ref{web2}.
In this way, the user can generate different passwords for
different services just by changing the seed string.
Seed strings like ``\textsf{Amazon123456}'' and ``\textsf{Facebook123456}'' are used
in the examples because users can easily remember
for which service the set of seeds and Q-A pairs are used.
Users don't have to remember the seed strings,
just like users don't have to remember the Q-A pairs.

@@

% David opinion
% \marginnote{The fact that an `old' memory is unlikely to be forgotten
%   is perhaps obvious, but this could be a good place to cite a paper
%   on memory/psychology about this if you're aware of any?}

% Frank:
% I second David's margin note. Can you back this claim--or more
% precisely the implied claim that old episodic memories will be
% unforgettable? (You could argue that no, you only said that IF the
% memory is old, episodic and unforgettable, THEN there's little chance
% to lose the password; you haven't said that IF the memory is old and
% episodic THEN it is unforgettable. Ok, ok, but then the question
% becomes: if I come up with and old and episodic memory, how do I know
% if it's a good one (unforgettable) or one that I will forget later? If
% you answer ``it never happens'' then you must back this claim. If it
% can happen, you should give me a criterion to tell in advance if it
% will, and why I should trust it.

@@

It can be difficult to provide a large number of false answers to a question like
``what is your favorite sport?''
because the number of possible answers is limited.
%
On the other hand, if the right answer to the question is a name of a place or a person,
generating similar answers is straightforward.
For example, if the answer to the question is ``Colorado'',
we can easily provide fake answers like ``California'', ``Utah'', {\it etc}.
because we can use the list of states in the U.S. as possible answers.

@@

% \marginnote{It may be helpful to give an indication of how many Q-A sets you think
% would be considered `sufficient' here.}
%
To prevent this, users can prefer saving questions and answers in a secret place or
use sufficient questions to prevent such a brute-force attack from being viable.
The entropy of 12 questions with 30 candidate answers 
is 58.9 ($12 \times \log_2 30$) bits, and this is considered to be safe
enough at this moment.

@@

Answering to many questions takes much longer time than typing a
remembered password, so people may prefer typing password
rather than using EpisoPass if they have to log in to a service frequently.
The tradeoff betwee security and usability has long been a big issue
of authentication systems \cite{Braz:2007:DTU:1778331.1778344},
but we believe we can approach the best solution by
improving the user interface of answering questions.

@@

The EpisoPass service is available via the Website and the source code is
available on GitHub\footnote{
  \url{https://EpisoPass.com/},
  \url{https://github.com/masui/EpisoPass}
}. EpisoPass currently has only a small user-base, one major
reason being that most people cannot fully understand the
idea behind EpisoPass, and may not trust it without the 
support of a well-known IT company.
% nor supported by famous computer users.
Another reason is that it's difficult for users to
assess the security of EpisoPass.
Since the intention is for the questions and answers to be obvious
to those that know them (but not to others), users may lack
confidence in their answers being unknown to others.
Any authentication system expecting widespread use must take
such psychological issues seriously, and we hope to address 
such issues in future work.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Acknowledgments.}

This paper was written while on
sabbatical at the University of Cambridge, hosted by Frank Stajano and
the Pico group, and supported by EPSRC grant number
EPSRC IRIS grant EP/M019055/1 on  ``Future Authentication Systems''.
%
We would like to thank Frank Stajano and David Llewellyn-Jones for
giving many valuable advices to our work.

\subsubsection*{Note.}

@@

\bibliographystyle{splncs03}
\bibliography{cameraready}

### 2016-12-11 paper/Password2016/david.tex
...

% \marginnote{I'd hesitate to call passwords the {\it strongest\/} method. Perhaps {\it most widely deployed\/} would be less contreversial?}
However, password-based authentication is still the most
convenient and widely deployed method \cite{Bonneau:ReplacePasswords},
and is not expected to disappear any time soon \cite{Herley:2009:PSS:1601990.1602010}.

@@

% \marginnote{You mention that episodic memories and cognitive passwords
%   have been used in the past, but it's not clear to me (from the text
%   here) why your system is different. Perhaps you could put a sentence
%   or two about this?}

The idea of using episodic memories for authentication has a long
history and early papers suggested using episodic memories for
creating passwords \cite{Barton:Password}.
Authentication using secret questions is sometimes
referred to as ``cognitive
passwords''\cite{Zviran:1990:UAC:100512.100538}, and such approaches
have been used as an alternative to password-based authentication
systems.
%
While cognitive passwords were aimed to be alternatives to
password-based systems, EpisoPass is a system for supporting
password-based systems using episodic memories.

@@

% \marginnote{Is the Android app generated as a unique app for each
%  user? If so, I think it's worth making this clear.}

If a user prefers not to use the EpisoPass service on the Web, there
is an alternative EpisoPass application for Android which requires no
network connection.  After registering questions and answers on the
EpisoPass service, the user can download an Android application from
the server by clicking the ``Android app'' button at the top of the
page.  The application unique to the user is compiled and built on the
server and contains all of the information needed for the particular
user to generate passwords using the Q-A sets entered.

@@

% \marginnote{The fact that an `old' memory is unlikely to be forgotten
%   is perhaps obvious, but this could be a good place to cite a paper
%   on memory/psychology about this if you're aware of any?}

@@

% \marginnote{In the comments you mention that ``generating
%   service-specific unique seed string is not trivial''. I think this
%   is worth mentioning in the paper.}

In the previous examples showing the author's EpisoPass questions, a
seed string ``\textsf{Amazon123456}'' was used for Amazon.com, and
``\textsf{Facebook123456}'' was used for Facebook.  Such strings were
chosen because they are easily memorable.  In practice any seed string
could be used as the seeds for the various services, and automatic
generation of seed strings is a possibility, although generating
service-specific unique seed string is not trivial.  For example,
users can use the same username and password both for Amazon.com and
Amazon.co.uk, but not for Amazon.co.jp.

@@

The strength of the generated passwords depends on the number and 
level of secrecy of the questions.
%
There have been many studies on the strength of passwords
\cite{Hayashi:2011:DSP:1978942.1979326,Komanduri:2011:PPM:1978942.1979321}, % What password is strong
but measuring the strength of secret questions is an area where more study is needed.
% \marginnote{I calculate $20^{10} = 10,240,000,000,000$. This is
% considerably more than a billion (closer to 10 thousand billion,
% (US) or 10 million million (UK).}
Using ten secret questions each with twenty answers, where each answer is considered equally likely,
an attacker would need to cover a search space of over ten trillion ($20^{10}$) values to check
every potential combination of answers,
and the entropy of the system is 43.2 ($10 \times \log_2 20$) bits.  % 10.0 * (Math.log(20.0)/Math.log(2.0))
%
This represents roughly the same entropy as using a random 8-character Latin-alphabet
password, for which the entropy is 45.6 bits.
This level is considered to be strong enough for Web services,
where it's not possible to perform online brute-force attacks \cite{Florencio:2007:SWP:1361419.1361429}.

@@

Users don't have to be very careful about handling questions and answers.
They can even be stored in a public place
given a sufficient number of questions and fake answers are provided.
%
Keeping secrets is a considerable effort for most people (including
the authors), but if the entire set of questions and answers used for EpisoPass
can stored publicly,
handling it becomes straightforward.
This is in contrast to the care needed when handling 
secrets like passwords, secret keys for SSH, {\it etc}. which should
never be copied to or saved in an unsafe place.
The EpisoPass data can be stored as a plain text file wherever is convenient
for the user, since a malicious attacker isn't able to generate
a valid password without also knowing the owner's relevant episodic memories.

@@

\subsection{Risk of server-side password leaks}

If one of the passwords generated by EpisoPass were to be revealed
for some reason, there is a danger that other passwords based on the same questions
might also be revealed.
%
For example, if Twitter is attacked by a hacker and
the password for Twitter (``\textsf{Lbasnln542202}'' in Figure \ref{web1})
is revealed to the attacker,
the attacker could test all answer combinations. If the attacker also had access
to the question and answer strings used, they could then establish the correct 
answers used to generate the password.
Once all the answers to the questions are known,
the attacker can then freely generate all of the user's passwords
generated from the same set of questions.

% \marginnote{It may be helpful to give an indication of how many Q-A sets you think
% would be considered `sufficient' here.}
%
To prevent this, it is safer to keep all of the questions and answers
in a secret place or
use sufficient questions to prevent such a brute-force attack from being viable.

@@

% \marginnote{The use of images is nice, but I don't find your argument
%   so convincing here. I have two concerns: first the claim that
%   selecting images will be easy. Second, the example you provide
%   doesn't seem strong, since other people are likely to be able to
%   identify a friend from a photograph.}

Pictures can also be used as EpisoPass questions,
similar to that shown at the bottom of Figure \ref{web1}.
Even if people find it difficult to create good secret questions,
selecting an image from their photo collections
and using it as the question should be straightforward.
For example, if you have an old special picture of a place you visited,
you can use it as the question and use the name of the place
as well as other similar fake place names.
For a secret question, a low-quality photo is better than a
high-quality photo because a low-quality photo
like the one shown in Figure \ref{web1} are not
easily recognizable by other people.

Of course, it's important the photo should have no information related
to the location, especially given how sophisticated
Web-based image searching has become.

\subsection{Password entry time}

Answering to many questions takes much longer time than typing a
remembered password, so most people may prefer typing password
rather than using EpisoPass if they have to log in to a service frequently.
The tradeoff betwee security and usability has long been a big issue
of authentication systems \cite{Braz:2007:DTU:1778331.1778344},
but we believe we can approach the best solution by
improving the user interface of answering questions.

% Frank's comment
% 3.11. It takes a rather long time to enter one password!''
% should also be discussed, and may be a killer in some cases. Maybe
% Episopass is good for infrequently used passwords where the penalty of
% a slow login is less relevant.

@@

As discussed in previous sections,
there have been many attempts to replace password-based authentication systems,
but none of them have yet become as widely deployed as
passwords \cite{Bonneau:ReplacePasswords}.
%
Although cognitive password systems have been an area of study for 
many years \cite{Lazar2011,Zviran:1990:UAC:100512.100538},
implementations up to now have all been intended as replacements 
to password-based systems, requiring support from the services involved.
As far as the authors are aware, ours is the first password-generation systems to be
based on cognitive authentication.

@@

The idea of using episodic memories for authentication is also not new.
In fact, using episodic memories for selecting passwords
has generally been recommended,
and many current computer users are probably using password that are
in some way informally related to their episodic memories.

Recent work has considered the use of mobile devices for authentication,
in particular harnessing the fact that a mobile device captures large quantities
of personal information. A mobile device may therefore be able to identify
its user based on their previous behavior; events which only the user would be able to recall \cite{Dandapat:2015:AYD:2702123.2702457,Das:2013:ECE:2493432.2493453,GuptaWRLGB12}%
.
For example, if a user can answer questions such as
``who did you call last night?'' correctly, the authentication will succeed.
Using mobile or wearable devices for authentication will become more usable
in the future,
but in order for this to work effectively users must be able to remember potentially
arbitrary behavior over the long-term. This may be a challenge for many people, and the 
benefit of EpisoPass in comparison is that the user is able to select memories that they
know to be memorable, rather than having their mobile device choose them arbitrarily.

Various types of image-based authentication systems have been proposed recently
\cite{Biddle:2012:GPL:2333112.2333114,GraphicalPasswords},
based on the realisation that images are easier to remember than text
given they are usually more directly linked to episodic memories.
However, some image-based authentication systems request
users to remember new secrets related to the images instead of
using the users' old episodic memories.
This turns out to be not much easier to remember than passwords.
%
% \marginnote{This statement seems to contradict what you said above
%   about it being easy to find images. Probably the phrasing just needs
%   a bit of refinement.}

Image-based authentication based on episodic memories might work
if users can prepare many images 
that are tightly linked to their episodic memories.
However, finding such images is usually not straightforward, and
image-only authentication systems are unlikely to become popular
until simple and effective techniques for doing so have been developed.

Even when a new ideal authentication method is invented,
replacing all the password-based systems will still be a lengthy process. 
Password managers will therefore remain important until this hypothetical
ideal solution has become ubiquitous.
In the age of password-based authentication,
using password managers seems to be the only way to tackle
the problem of passwords.
%
While most of the password managers only remember passwords given by the user,
generating passwords with a password manager is a new approach for
handling password-based systems.
Just like EpisoPass generates passwords,
Versipass \cite{Stobert:2014:PMD:2683467.2683471} %Versipass 画像のヒントからパスワード生成 % A Password Manager that Doesn’t Remember
helps the user to generate password strings
using ``visual cues'' from an arbitrary image.
Instead of directly using images for authentication,
users use the system to generate a password string with the help of
the image shown to the user.

@@

EpisoPass has been used by the authors for more than three years
for various services including Twitter, Facebook, Amazon, Skype, {\it etc}.
% Since passwords for these services are remembered on the browser,
% EpisoPass is used only once in one week at most.
%
Before using EpisoPass, managing multiple passwords was a significant challenge
for the authors. We now have all the information for generating passwords 
stored in the cloud and no problems have arisen during this period.
%
Since the introduction of our browser extension, visiting the EpisoPass 
service has now become unnecessary, making authentication to the various
services even easier.

The EpisoPass service is available via the Website and the source code is
available on GitHub\footnote{
  (url removed for double-blind review)
  % \url{https://EpisoPass.com/},
  % \url{https://github.com/masui/EpisoPass}
}. EpisoPass currently has only a small user-base, one major
reason being that most people cannot fully understand the
idea behind EpisoPass, and may not trust it without the 
support of a well-known IT company.
% nor supported by famous computer users.
Another reason is that it's difficult for users to
assess the security of EpisoPass.
Since the intention is for the questions and answers to be obvious
to those that know them (but not to others), users may lack
confidence in their answers being unknown to others.
Any authentication system expecting widespread use must take
such psychological issues seriously, and we hope to address 
such issues in future work.

@@

We introduced a password management system {\it EpisoPass\/}
that converts a seed string into a password using the user's
episodic memories. These memories are represented as a set of questions and answers
which can be solved only by the user in order to generate a site-specific password.
%
Using EpisoPass with well-defined questions and answers,
a user can always retrieve a service's passwords without worrying about
having to remember any secret information, other than the episodic memories
that have been chosen specifically to be easy to recall.
%
In future work we hope to integrate the system with more existing password-based
services, and ultimately aim to address the problems
derived from password-based authentication.

@@

This paper is largely a translation of a 2013 paper published by the
author in Japanese \cite{WISS2013}. This is the first time that the
work is presented to an international audience in English.
Additionally, in the intervening three years the author has
developed the browser extension described in section \ref{extensionsection}.

@@

% \marginnote{I've added some text in about the grant. Please change it
%   as you see fit of course. I'm afraid I don't know the grant number
%   so have left a gap; ideally this should be added in too.}

% \subsubsection*{Acknowledgments.}
% This paper was written while on
% sabbatical at the University of Cambridge, hosted by Frank Stajano and
% the Pico group, and supported by EPSRC grant number
% EPSRC IRIS grant EP/M019055/1 on  ``Future Authentication Systems''.

>>>>

\marginnote{I'd hesitate to call passwords the {\it strongest\/} method. Perhaps {\it most widely deployed\/} would be less contreversial?}
However, password-based authentication is still the most
convenient and widely deployed method \cite{Bonneau:ReplacePasswords},
and is not expected to disappear any time soon \cite{Herley:2009:PSS:1601990.1602010}.

@@

\marginnote{You mention that episodic memories and cognitive passwords have been used in the past, but it's not clear to me (from the text here) why your system is different. Perhaps you could put a sentence or two about this?}

The idea of using episodic memories for authentication has a long history and early papers suggested using episodic memories for creating passwords. Authentication using secret questions is sometimes referred to as ``cognitive passwords''\cite{Zviran:1990:UAC:100512.100538}, and such approaches have been used as an alternative to password-based authentication systems.
%
% However, conversion from episodic memories to password strings
% was not studied at all.

@@

\marginnote{Is the Android app generated as a unique app for each user? If so, I think it's worth making this clear.}
If a user prefers not to use the EpisoPass service on the Web,
there is an alternative EpisoPass application for Android
which requires no network connection.
After registering questions and answers on the EpisoPass service,
the user can download an Android application from the server
by clicking the ``Android app'' button at the top of the page.
The application is compiled and built on the server and contains
all of the information needed for the particular user to
generate passwords using the Q-A sets entered.

@@

\marginnote{The fact that an `old' memory is unlikely to be forgotten is perhaps obvious, but this could be a good place
to cite a paper on memory/psychology about this if you're aware of any?}

@@

\marginnote{In the comments you mention that ``generating service-specific unique seed string is not trivial''. I think this is worth mentioning in the paper.}

In the previous examples showing the author's EpisoPass questions,
a seed string ``\textsf{Amazon123456}'' was used for Amazon.com, and
``\textsf{Facebook123456}'' was used for Facebook.
Such strings were chosen because they are easily memorable.
In practice any seed string could be used as the seeds for the various services,
and automatic generation of seed strings is a possibility.

% although generating service-specific unique seed string is not trivial.
% For example, users can use the same username and password both
% for Amazon.com and Amazon.co.uk, but not for Amazon.co.jp.

@@

The strength of the generated passwords depends on the number and 
level of secrecy of the questions.
%
There have been many studies on the strength of passwords
\cite{Hayashi:2011:DSP:1978942.1979326,Komanduri:2011:PPM:1978942.1979321}, % What password is strong
but measuring the strength of secret questions is an area where more study is needed.
%
\marginnote{I calculate $20^{10} = 10,240,000,000,000$. This is considerably more than a billion (closer to 10 thousand billion, (US) or 10 million million (UK).}
%
Using ten secret questions each with twenty answers, where each answer is considered equally likely,
an attacker would need to cover a search space of over a billion ($20^{10}$) values to check
every potential combination of answers,
and the entropy of the system is 43.2 ($10 \times \log_2 20$) bits.  % 10.0 * (Math.log(20.0)/Math.log(2.0))
%
This represents roughly the same entropy as using a random 8-character Latin-alphabet
password, for which the entropy is 45.6 bits.
This level is considered to be strong enough for Web services,
where it's not possible to perform online brute-force attacks \cite{Florencio:2007:SWP:1361419.1361429}.

@@

Users don't have to be very careful about handling questions and answers.
They can even be put on a public place
if enough amount of questions and fake answers are provided.
%
Keeping secrets is always a pain for many people including
the authors, but if the whole questions and answers used on EpisoPass
can be put on a public place,
handling it becomes very easy.
Usually we have to be very careful about handling
secret information like passwords, secret key for SSH, etc.
because they should not be copied or saved at unsafe places.
On the other hand,
we can save the EpisoPass data as a plain text file and put it at
any place without great care, since malicious person cannot calculate
passwords without having the owner's episodic memories.

@@

\subsection{Risk of password leak at the service side}

If one of the passwords generated by EpisoPass is revealed
for some reason, other passwords based on the same questions
might also be revealed.
%
For example, if Twitter is attacked by a cracker and
the password for Twitter (``\textsf{Lbasnln542202}'' in Figure \ref{web1})
is revealed to the attacker,
the attacker can try all the answer combinations and find out
the answers to all the questions,
if questions and answers are also known by the attacker.
Once all the answers to the questions are known,
the attacker can freely generate all the passwords
generated with the same questions.

To prevent such trouble, it is safer to keep all the questions and answers
in a secret place or
use sufficient number of questions so that brute-force does not work.

@@

Old pictures can be used as the questions of EpisoPass,
just like the question shown at the bottom of Figure \ref{web1}.
Even when people cannot create good secret questions,
people can fairly easily select a secret image from their photo collections
and use it as the question.
For example, if you have an old picture of your friend,
you can use it as the question
and use his real name as well as other similar fake names.

% 画像検索とかされないようにする必要はある

Of course, the photo should not have information related to the
person's real name, since image search is fairly easy on the Web these days.

@@

As shown in previous sections,
there have been many attempts for replacing password-based authentication systems,
but none of them are found to be better than
password-based systems\cite{Bonneau:ReplacePasswords}.
%
Although cognitive password systems have been studied for a
long time\cite{Lazar2011}\cite{Zviran:1990:UAC:100512.100538},
they were implemented as a replacement to password-based systems,
and no password-generation system have been proposed
based on cognitive authentication.

@@

The idea of using episodic memories for authentication is not new.
In fact, using episodic memories for selecting password
has generally been recommended,
and many current computer users are probably using password that are
in some way related to their episodic memories.

Recently, people are trying to use mobile devices for authentication,
because mobile devices remember all the user's behaviors and
the user can easily recall what he did%
\cite{Dandapat:2015:AYD:2702123.2702457}%
\cite{Das:2013:ECE:2493432.2493453}%
\cite{GuptaWRLGB12}%
.
For example, if a user can answer questions like
``who did you call last night?'' correctly, the authentication will succeed.
Using mobile or wearable devices for authentication will become more usable
in the future,
but users should have a fairly good long-term memory about their behaviors,
and that not easy for everybody.

Various types of image-based authentication systems have been proposed recently%
\cite{Biddle:2012:GPL:2333112.2333114}\cite{GraphicalPasswords},
in the hope that images are easier to remember than text
because images are usually more directly linked to episodic memories.
However, on many systems,
users have to remember new information related to the images
used in the authentication process, or
perform special operations on the image, and
it is not much easier than remembering passwords.
%
Image-based authentication based on episodic memories might work
if anyone can prepare many images 
that are tightly linked to his episodic memories.
However, finding such images is usually not easy, and
image-only authentication systems would not take off
until simple and effective technique is invented.

Even when a new ideal authentication method is invented,
replacing all the password-based systems should take very long, and
various password managers should be used until the ideal method
prevails in the world.
In the age of password-based authentication,
using password managers seems to be the only way to tackle
the problem of passwords.
%
While most of the password managers only remember passwords given by the user,
generating passwords with a password manager is a new approach for
handling password-based systems.
Just like EpisoPass generates passwords,
Versipass\cite{Stobert:2014:PMD:2683467.2683471} %Versipass 画像のヒントからパスワード生成 % A Password Manager that Doesn’t Remember
helps the user to generate password strings
using ``visual cues'' on an arbitrary image.
Instead of directly using images for authentication,
users use the system to generate a password text with the help of
the image shown to the user.

@@

EpisoPass has been used by the authors for more than three years, and
the authors are using it for various services including
Twitter, Facebook, Amazon, Skype, etc.
% Since passwords for these services are remembered on the browser,
% EpisoPass is used only once in one week at most.
%
Before using EpisoPass, taking care of many passwords was really
a pain for the authors, but
currently all the information for generating passwords is put on the cloud
and no trouble has been found during the period.
%
After the introduction of browser extension,
logging into various services became even easier,
because visiting the EpisoPass service is unneccesary.

EpisoPass service have been on the Web and the source code is
available on GitHub\footnote{
  (url removed for double-blind review)
  % \url{https://EpisoPass.com/},
  % \url{https://github.com/masui/EpisoPass}
}, but
unfortunately EpisoPass is currently not used by many people.
One big reason is that most people cannot fully understand the
idea of EpisoPass and also cannot fully trust it
because it is not operated by a big IT company.
% nor supported by famous computer users.
Another reason might be that users cannot estimate the strength
of EpisoPass.
Since all the questions and answers are
quite obvious to the users,
they might feel that everyone else also know the episode
and easily solve all the questions.
These kinds of psychological issues are quite important for
an authentication system for everybody,
and we hope to eliminate such obstacles in the future.

@@

We introduced a password management system EpisoPass
that converts a seed string into a password using the user's
episodic memories represented as a set of questions and answers
which can be solved only by the user.
%
Using EpisoPass with well-defined questions and answers,
a user can always retrieve various passwords without worrying about
remembering secret information.
%
We'll try to integrate the system with existing password-based
services, and finally hope to eliminate all the problems
derived from password-based authentication.

@@

This paper is largely a translation of a 2013 paper published by the
author in Japanese\cite{WISS2013}. This is the first time that the
work is presented to an international audience in English.
Additionally, in the intervening three years the author has
developed the browser extension described in section \ref{extensionsection}.

@@

\subsubsection*{Acknowledgments.} The heading should be treated as a
subsubsection heading and should not be assigned a number.
